DSSynth: An Automated Synthesis Tool for Physical Plants \\ Digital Controllers via MATLAB Toolbox

### 2017-05-31 emsoft2017/emsoft-paper.tex
reviewed section 2.1
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

\keywords{Formal Synthesis, Digital Controllers, MATLAB Toolbox, Fixed-point Arithmetic, Transfer-Function, State-Space, Digital Control Synthesis}

@@

%---------------------------------------------------
\section{Synthesizing Digital Controller with \tool}
%---------------------------------------------------

@@

The proposed synthesization methodology for closed-loop digital systems is based on DSSynth~\cite{abate2017, abatecav2017} and it can be split into two main stages as follows: manual (user) and automated (DSSynth) procedures, as shown in Fig.~\ref{fig:synthesis-flow}.

\begin{figure}[ht!]
\centering
\includegraphics[width=0.45\textwidth]{synthesis-flow.pdf}
\caption{Digital-Control Synthesis Methodology.}
\label{fig:synthesis-flow}
\end{figure}

In step $1$, the digital-control representation is determined, and it could be in transfer-function or state-space equations. In step $2$, the physical plant with the coefficients must be designed according to equations (\ref{eq:transferfunction}) and (\ref{eq:ss-example}). And finally, in step $3$, the numerical representation with the digital-control implementation must be defined, {\it i.e.}, the FWL format that includes the number of bits in the integer and fractional parts and the dynamic range inputs. The result from the manual procedure is a digital-system implementation for the given physical plant in MATLAB.

The synthesis process starts in step $A$, when the \tool gets the digital-system in MATLAB, and then translate it in a ANSI-C program, and then in step $B$, the DSSynth Tool is invoked. Finally, in step $C$, the digital controller is synthesized based on (CEGIS)~\cite{DBLP:conf/asplos/Solar-LezamaTBSS06}. The output generated in MATLAB is the digital controller synthesized, and it could be represented in transfer-function or state-space format. The synthesis is \emph{successful} when a digital controller is synthesized correctly, and the synthesis has status \emph{failed} when any parameter is defined incorrectly in previous steps, or there is no solution for the digital-system designed.

>>>>

\keywords{Formal Synthesis; Digital Control Systems; MATLAB Toolbox; Finite-Word Length; Verification}

@@

%---------------------------------------------------
\section{Synthesizing Digital Controllers with \tool}
%---------------------------------------------------

@@

The proposed synthesis methodology for closed-loop digital control
systems is based on the DSSynth tool~\cite{abate2017, abatecav2017}; 
it can be split into two main stages as follows: manual (user) and 
automated (DSSynth) procedures, as illustrated in Fig.~\ref{fig:synthesis-flow}. 
%
\begin{figure}[ht!]
\centering
\includegraphics[width=0.45\textwidth]{synthesis-flow.pdf}
\caption{Digital Controller Synthesis Methodology.}
\label{fig:synthesis-flow}
\end{figure}

In step $1$, the digital-control representation is define, which can be in 
transfer-function or state-space equations. In step $2$, the physical plant 
with the respective coefficients must be designed, according to equations 
(\ref{eq:transferfunction}) and (\ref{eq:ss-example}). And finally, in step $3$, 
the numerical representation for the digital controller implementation must be 
defined, {\it i.e.}, the FWL format that includes the number of bits for the integer 
and fractional parts and the dynamic range inputs. The results from the manual 
procedure is a digital-system implementation for the given physical plant in MATLAB.

The synthesis process starts in step $A$, when the \tool gets the digital-system in MATLAB, 
and then translates it into a ANSI-C program; then in step $B$, the DSSynth Tool is invoked. 
Finally, in step $C$, the digital controller is synthesized based on CEGIS. The output generated 
in MATLAB is the synthesized digital controller, which can be represented in transfer-function 
or state-space format. The synthesis is \emph{successful} if a digital controller is correctly synthesized;
otherwise the synthesis has status \emph{failed} if any parameter is defined incorrectly 
in previous steps, or there is no solution for the designed digital controller.
